Market simulator

### 2023-08-26 analysis/01_experimental-design.Rmd

# Dummy-coded interactions

We have a number of hypotheses referencing specific interactions. To answer these hypotheses, we need to specific each of the needed interactions.

@@

# Index-code the design

Now we prepare the experimental design for use in estimating the model by keeping each level of each attribute, which are all discrete. An index-coded design has no reference levels.

```{r index-design, warning=FALSE, message=FALSE}
# Convert the attributes in design into factors
index_design <- as.data.frame(design)
for(i in 4:ncol(index_design)) {
  index_design[,i] <- as.factor(index_design[,i])
}

@@

# Index-coded interactions

We have a number of hypotheses referencing specific interactions. To answer these hypotheses, we need to specific each of the needed interactions.

```{r index-interactions, warning=FALSE, message=FALSE}
# Convert the attributes in design into factors
interactions <- as.data.frame(design)
for(i in 4:ncol(interactions)) {
  interactions[,i] <- as.factor(interactions[,i])
}

@@

    # # Hypothesis 2b.
    # amnesty_criticized = org1 * gov_rel2,
    # greenpeace_criticized = org2 * gov_rel2,
    # oxfam_criticized = org3 * gov_rel2,
    # redcross_criticized = org4 * gov_rel2,
    # amnesty_crackdown = org1 * gov_rel3,
    # greenpeace_crackdown = org2 * gov_rel3,
    # oxfam_crackdown = org3 * gov_rel3,
    # redcross_crackdown = org4 * gov_rel3,

@@

    refugees_crackdown = issue4 * gov_rel3
    # # Hypothesis 4b.
    # wealthydonors_criticized = fund2 * gov_rel2,
    # govgrants_criticized = fund3 * gov_rel2,
    # wealthydonors_crackdown = fund2 * gov_rel3,
    # govgrants_crackdown = fund3 * gov_rel3,
    # # Hypothesis 4c.
    # emergency_wealthydonors_crackdown = issue1 * fund2 * gov_rel3, # ??????
    # emergency_govgrants_crackdown = issue1 * fund3 * gov_rel3,     # ??????
    # environment_wealthydonors_crackdown = issue2 * fund2 * gov_rel3,
    # environment_govgrants_crackdown = issue2 * fund3 * gov_rel3,
    # humanrights_wealthydonors_crackdown = issue3 * fund2 * gov_rel3,
    # humanrights_govgrants_crackdown = issue3 * fund3 * gov_rel3,
    # refugees_wealthydonors_crackdown = issue4 * fund2 * gov_rel3,
    # refugees_govgrants_crackdown = issue4 * fund3 * gov_rel3,
    # # Hypothesis 5b.
    # transp_criticized = transp2 * gov_rel2,
    # transp_crackdown = transp2 * gov_rel3,
    # # Hypothesis 5c.
    # transp_smalldonors_criticized = transp2 * fund1 * gov_rel2,
    # transp_wealthydonors_criticized = transp2 * fund2 * gov_rel2,
    # transp_govgrants_criticized = transp2 * fund3 * gov_rel2,
    # transp_smalldonors_crackdown = transp2 * fund1 * gov_rel3,
    # transp_wealthydonors_crackdown = transp2 * fund2 * gov_rel3,
    # transp_govgrants_crackdown = transp2 * fund3 * gov_rel3,
    # # Hypothesis 5d.
    # transp_emergency_criticized = transp2 * issue1 * gov_rel2,
    # transp_emergency_crackdown = transp2 * issue1 * gov_rel3,
    # transp_environment_criticized = transp2 * issue2 * gov_rel2,
    # transp_environment_crackdown = transp2 * issue2 * gov_rel3,
    # transp_humanrights_criticized = transp2 * issue3 * gov_rel2,
    # transp_humanrights_crackdown = transp2 * issue3 * gov_rel3,
    # transp_refugees_criticized = transp2 * issue4 * gov_rel2,
    # transp_refugees_crackdown = transp2 * issue4 * gov_rel3,
    # # Hypothesis 5e.
    # transp_smalldonors_emergency_criticized = transp2 * fund1 * issue1 * gov_rel2,
    # transp_smalldonors_emergency_crackdown = transp2 * fund1 * issue1 * gov_rel3,
    # transp_smalldonors_environment_criticized = transp2 * fund1 * issue2 * gov_rel2,
    # transp_smalldonors_environment_crackdown = transp2 * fund1 * issue2 * gov_rel3,
    # transp_smalldonors_humanrights_criticized = transp2 * fund1 * issue3 * gov_rel2,
    # transp_smalldonors_humanrights_crackdown = transp2 * fund1 * issue3 * gov_rel3,
    # transp_smalldonors_refugees_criticized = transp2 * fund1 * issue4 * gov_rel2,
    # transp_smalldonors_refugees_crackdown = transp2 * fund1 * issue4 * gov_rel3

@@

# Aggregate-coded interactions

We have a number of hypotheses referencing specific interactions. To answer these hypotheses, we need to specific each of the needed interactions. Here we do it by aggregating up the interaction terms.

```{r aggregate-interactions, warning=FALSE, message=FALSE}
# Convert the attributes in design into factors
interactions <- as.data.frame(design)
for(i in 4:ncol(interactions)) {
  interactions[,i] <- as.factor(interactions[,i])
}

@@

# # org1 = amnesty
# # org2 = greenpeace
# # org3 = oxfam
# # org4 = redcross
# # gov_rel1 = friendly
# # gov_rel2 = criticized
# # gov_rel3 = crackdown
# 
# # Build out all the necessary interactions...
# # ...by multiplying together the needed index-coded levels.
# interactions <- interactions %>% 
#   as_tibble() %>% 
#   mutate(
#     h2b_1 = ifelse(Organization ==3|Organization==4, 1, 0), # 1 if org is oxfam or redcross
#     h2b_2 = ifelse(`Relationship with host government` == 2|`Relationship with host government` == 3, 1, 0), # 1 if gov_rel is criticized or crackdown
#     h2b_3 = h2b_1*h2b_2 # interaction term
#     )

interactions <- interactions |> 
  mutate(
    # Oxfam or Red Cross.
    h2b_org_1 = ifelse(org3 == 1 | org4 == 1, 1, 0),
    # Government crackdown or criticism.
    h2b_gov_rel_1 = ifelse(gov_rel2 == 1 | gov_rel3 == 1, 1, 0),
    # Oxfam or Red Cross facing government crackdown or criticism.
    h2b_int_1 = ifelse(org3 == 1 | org4 == 1, 1, 0) * ifelse(gov_rel2 == 1 | gov_rel3 == 1, 1, 0),
    # Amnesty or Greenpeace.
    h2b_org_2 = ifelse(org1 == 1 | org2 == 1, 1, 0),
    # Government crackdown.
    h2b_gov_rel_2 = gov_rel3,
    # Amnesty or Greenpeace is facing crackdown.
    # h2b_2 = ifelse(org1 == 1 | org2 == 1, 1, 0) * gov_rel3
    h2b_int_2 = ifelse(org1 == 1 | org2 == 1, 1, 0) * gov_rel3
  )
  # select(1:3, contains("h2b"))

# interactions |> 
#   # select(org1:org4, gov_rel2:gov_rel3, h2b_1, h2b_2)
#   # select(org3, org4, gov_rel2, gov_rel3, h2b_1)
#   select(org1, org2, gov_rel3, h2b_2)
# interactions <- interactions %>% 
#   as_tibble() %>% 
#   mutate(
#     # Hypothesis 2b.
#     amnesty_criticized = org1 * gov_rel2,
#     greenpeace_criticized = org2 * gov_rel2,
#     oxfam_criticized = org3 * gov_rel2,
#     redcross_criticized = org4 * gov_rel2,
#     amnesty_crackdown = org1 * gov_rel3,
#     greenpeace_crackdown = org2 * gov_rel3,
#     oxfam_crackdown = org3 * gov_rel3,
#     redcross_crackdown = org4 * gov_rel3,
#     # Hypothesis 3b.
#     environment_criticized = issue2 * gov_rel2,
#     humanrights_criticized = issue3 * gov_rel2,
#     refugees_criticized = issue4 * gov_rel2,
#     environment_crackdown = issue2 * gov_rel3,
#     humanrights_crackdown = issue3 * gov_rel3,
#     refugees_crackdown = issue4 * gov_rel3,
#     # Hypothesis 4b.
#     wealthydonors_criticized = fund2 * gov_rel2,
#     govgrants_criticized = fund3 * gov_rel2,
#     wealthydonors_crackdown = fund2 * gov_rel3,
#     govgrants_crackdown = fund3 * gov_rel3,
#     # Hypothesis 4c.
#     emergency_wealthydonors_crackdown = issue1 * fund2 * gov_rel3, # ??????
#     emergency_govgrants_crackdown = issue1 * fund3 * gov_rel3,     # ??????
#     environment_wealthydonors_crackdown = issue2 * fund2 * gov_rel3,
#     environment_govgrants_crackdown = issue2 * fund3 * gov_rel3,
#     humanrights_wealthydonors_crackdown = issue3 * fund2 * gov_rel3,
#     humanrights_govgrants_crackdown = issue3 * fund3 * gov_rel3,
#     refugees_wealthydonors_crackdown = issue4 * fund2 * gov_rel3,
#     refugees_govgrants_crackdown = issue4 * fund3 * gov_rel3,
#     # Hypothesis 5b.
#     transp_criticized = transp2 * gov_rel2,
#     transp_crackdown = transp2 * gov_rel3,
#     # Hypothesis 5c.
#     transp_smalldonors_criticized = transp2 * fund1 * gov_rel2,
#     transp_wealthydonors_criticized = transp2 * fund2 * gov_rel2,
#     transp_govgrants_criticized = transp2 * fund3 * gov_rel2,
#     transp_smalldonors_crackdown = transp2 * fund1 * gov_rel3,
#     transp_wealthydonors_crackdown = transp2 * fund2 * gov_rel3,
#     transp_govgrants_crackdown = transp2 * fund3 * gov_rel3,
#     # Hypothesis 5d.
#     transp_emergency_criticized = transp2 * issue1 * gov_rel2,
#     transp_emergency_crackdown = transp2 * issue1 * gov_rel3,
#     transp_environment_criticized = transp2 * issue2 * gov_rel2,
#     transp_environment_crackdown = transp2 * issue2 * gov_rel3,
#     transp_humanrights_criticized = transp2 * issue3 * gov_rel2,
#     transp_humanrights_crackdown = transp2 * issue3 * gov_rel3,
#     transp_refugees_criticized = transp2 * issue4 * gov_rel2,
#     transp_refugees_crackdown = transp2 * issue4 * gov_rel3,
#     # Hypothesis 5e.
#     transp_smalldonors_emergency_criticized = transp2 * fund1 * issue1 * gov_rel2,
#     transp_smalldonors_emergency_crackdown = transp2 * fund1 * issue1 * gov_rel3,
#     transp_smalldonors_environment_criticized = transp2 * fund1 * issue2 * gov_rel2,
#     transp_smalldonors_environment_crackdown = transp2 * fund1 * issue2 * gov_rel3,
#     transp_smalldonors_humanrights_criticized = transp2 * fund1 * issue3 * gov_rel2,
#     transp_smalldonors_humanrights_crackdown = transp2 * fund1 * issue3 * gov_rel3,
#     transp_smalldonors_refugees_criticized = transp2 * fund1 * issue4 * gov_rel2,
#     transp_smalldonors_refugees_crackdown = transp2 * fund1 * issue4 * gov_rel3
#   )

>>>>

# Code all possible interactions

We have a number of hypotheses referencing specific interactions. To answer these hypotheses, we need to specify each of the needed interactions.

@@

# Index-coded experimental alternative

It's possible an index-coded design will serve us better, allowing us to compute whatever contrasts are needed from a single model. An index-coded design has no reference levels.

```{r index-design, warning=FALSE, message=FALSE}
################################################################################
# This is an experimental alternative to the dummy-coded design.
################################################################################

# Convert the attributes in design into factors
index_design <- as.data.frame(design)
for(i in 4:ncol(index_design)) {
  index_design[,i] <- as.factor(index_design[,i])
}

@@

We have a number of hypotheses referencing specific interactions. To answer these hypotheses, we need to specify each of the needed interactions.

```{r index-interactions, warning=FALSE, message=FALSE}
################################################################################
# This is an experimental alternative to the interactions based on the 
# dummy-coded design.
################################################################################

# Convert the attributes in design into factors
interactions <- as.data.frame(design)
for(i in 4:ncol(interactions)) {
  interactions[,i] <- as.factor(interactions[,i])
}

@@

@@

    smalldonors_criticized = fund1 * gov_rel2,
    smalldonors_crackdown = fund1 * gov_rel3,
    emergency_smalldonors_crackdown = issue1 * fund1 * gov_rel3,
    environment_smalldonors_crackdown = issue2 * fund1 * gov_rel3,
    humanrights_smalldonors_crackdown = issue3 * fund1 * gov_rel3,
    refugees_smalldonors_crackdown = issue4 * fund1 * gov_rel3,
    nottransp_criticized = transp1 * gov_rel2,
    nottransp_crackdown = transp1 * gov_rel3,
    nottransp_smalldonors_criticized = transp1 * fund1 * gov_rel2,
    nottransp_wealthydonors_criticized = transp1 * fund2 * gov_rel2,
    nottransp_govgrants_criticized = transp1 * fund3 * gov_rel2,
    nottransp_smalldonors_crackdown = transp1 * fund1 * gov_rel3,
    nottransp_wealthydonors_crackdown = transp1 * fund2 * gov_rel3,
    nottransp_govgrants_crackdown = transp1 * fund3 * gov_rel3,
    nottransp_emergency_criticized = transp1 * issue1 * gov_rel2,
    nottransp_emergency_crackdown = transp1 * issue1 * gov_rel3,
    nottransp_environment_criticized = transp1 * issue2 * gov_rel2,
    nottransp_environment_crackdown = transp1 * issue2 * gov_rel3,
    nottransp_humanrights_criticized = transp1 * issue3 * gov_rel2,
    nottransp_humanrights_crackdown = transp1 * issue3 * gov_rel3,
    nottransp_refugees_criticized = transp1 * issue4 * gov_rel2,
    nottransp_refugees_crackdown = transp1 * issue4 * gov_rel3,
    nottransp_smalldonors_emergency_criticized = transp1 * fund1 * issue1 * gov_rel2,
    nottransp_smalldonors_emergency_crackdown = transp1 * fund1 * issue1 * gov_rel3,
    nottransp_smalldonors_environment_criticized = transp1 * fund1 * issue2 * gov_rel2,
    nottransp_smalldonors_environment_crackdown = transp1 * fund1 * issue2 * gov_rel3,
    nottransp_smalldonors_humanrights_criticized = transp1 * fund1 * issue3 * gov_rel2,
    nottransp_smalldonors_humanrights_crackdown = transp1 * fund1 * issue3 * gov_rel3,
    nottransp_smalldonors_refugees_criticized = transp1 * fund1 * issue4 * gov_rel2,
    nottransp_smalldonors_refugees_crackdown = transp1 * fund1 * issue4 * gov_rel3,

@@

## Aggregate-coded interaction alternative

```{r aggregate-interactions, warning=FALSE, message=FALSE}
################################################################################
# This is an experimental alternative where specific contrasts are estimated
# as part of the model (hence aggregate-coded) rather than computed using
# marginal posteriors after estimation.
################################################################################

# Convert the attributes in design into factors
interactions <- as.data.frame(design)
for(i in 4:ncol(interactions)) {
  interactions[,i] <- as.factor(interactions[,i])
}

@@

################################################################################
# Are we sure this is encoding the needed contrasts exactly??
################################################################################

# # Build out all the necessary interactions...
# # ...by multiplying together the needed index-coded levels.
# org1 = amnesty
# org2 = greenpeace
# org3 = oxfam
# org4 = redcross
# gov_rel1 = friendly
# gov_rel2 = criticized
# gov_rel3 = crackdown
# issue1 = emergency
# issue2 = environment
# issue3 = human rights
# issue4 = refugee
# transp1 = not transparent
# transp2 = transparent
# account1 = not accountable
# account2 = accountable
# fund1 = smalldonors
# fund2 = wealthydonors
# fund3 = gov grants

# Sticking exactly to the hypotheses where each contrasts will 
# consist of h*_high - h*_low
interactions <- interactions %>% 
  as_tibble() %>% 
  rowwise() %>% 
  mutate(
    # Main effects
    h1_high = sum(org3, org4), # oxfam and red cross
    h1_low = sum(org1, org2), # amnesty and greenpeace
    h2a_high = sum(gov_rel2,gov_rel3), # criticized and crackdown
    h2a_low = gov_rel1, # friendly
    h3a_high = sum(issue1, issue4), # emergency and refugee
    h3a_low = sum(issue2, issue3), # environment and human rights
    h4a_high = fund1, # small donors
    h4a_low = sum(fund2, fund3), # wealthy donors and gov grants
    h5a_high = transp2, # transparent
    h5a_low = transp1, # not transparent
    # First-order Interactions
    h2b_high = h1_high*h2a_high, #  oxfam and red cross * criticized and crackdown
    h2b_low = h1_low*gov_rel3, # amnesty and greenpeace * criticized
    h3b_high = h2a_high*h3a_high, # criticized and crackdown * emergency and refugee
    h3b_low = h2a_high*h3a_low, # criticized and crackdown * environment and human rights
    h4b_high = gov_rel3*fund1, # crackdown * small donors
    h4b_low = sum(gov_rel1, gov_rel2)*h4a_high, # not crackdown * not small donors
    h5b_high = h2a_high*h5a_high, # criticized and crackdown * transparent
    h5b_low = h5a_low + h2a_low*h5a_high, # not transparent + friendly * transparent + 
    # Second-order interactions
    h4c_high = gov_rel3*h4a_high*h3a_high, # crackdown * small donors * emergency and refugee
    h4c_low = ifelse(h4c_high==1, 0, 1), # everything else
    h5c_high = h2a_high*h5a_high*h4a_high, # criticized and crackdown * transparent * small donors
    h5c_low = ifelse(h5c_high==1, 0, 1), # everything else
    h5d_high = h2a_high*h5a_high*h3a_high, # criticized and crackdown * transparent * emergency and refugee
    h5d_low = ifelse(h5d_high==1, 0, 1), # everything else
    # Third-order interaction
    h5e_high = h2a_high*h5a_high*h3a_high*h4a_high, # criticized and crackdown * transparent * emergency and refugee * small donors
    h5e_low = ifelse(h5e_high==1, 0, 1)) %>% 
  ungroup()

### 2023-08-26 analysis/02_clean-data.Rmd

>>>>

# # If I could rename the 13 X columns
# dummy_level_labels <- c(
#   str_c("Organization: ", c("Amnesty International", "Greenpeace", "Oxfam", "Red Cross")),
#   str_c("Issue area: ", c("Environment", "Human rights", "Refugee relief")),
#   str_c("Organizational practices: ", c("Financial transparency", "Accountability")),
#   str_c("Funding sources: ", c("Handful of wealthy private donors", "Government grants")),
#   str_c("Relationship with host government: ", c("Criticized", "Under crackdown"))
# )

### 2023-08-26 analysis/05_market-simulator.Rmd

```{r load-data, message=FALSE}
# Gammas of the "everything" model
gammas <- read_rds(
    here::here('analysis', 'output', 'posterior_draws', 'public_political_social_charity_demo.rds')
  ) %>% 
  group_by(i, j) %>% 
  summarize(gamma_mean = mean(Gamma)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = j, values_from = gamma_mean) %>% 
  select(-i) %>% 
  t()

>>>>

```{r load-data, message=FALSE}
# Gammas of the "everything" model
gammas <- read_rds(
    here::here('data', 'raw_data', 'posterior_draws', 'public_political_social_charity_demo.rds')
  ) %>% 
  group_by(i, j) %>% 
  summarize(gamma_mean = mean(Gamma)) %>% 
  ungroup() %>% 
  pivot_wider(names_from = j, values_from = gamma_mean) %>% 
  select(-i) %>% 
  t()
